Named Entity Recognition with Structured Prediction

### 2012-11-07 doc/report/paper.tex
Minor paper changes.

\documentclass[11pt]{article}
\usepackage{acl2011}
\usepackage[utf8]{inputenc}
\usepackage{linguex}
\usepackage{latexsym}  
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{verbatim}
\usepackage{array}
\usepackage{subfigure}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{qtree}
%\usepackage{gb4e}

@@

@@

\exg. \textbf{x:} The motor company ' Ford ' was founded and incorporated by Henry Ford .\\
      \textbf{y:} O O O O ORG  O  O O O O O PER PER O  \label{PredEx1b} \\

@@

Learning is implemented using the Structured Perceptron algorithm. To avoid overfitting, we average the parameters after the last iteration \cite{collins2002discriminative}. For finding the best sequence of labels, we use a modified version of the Viterbi algorithm. The algorithm finds the sequence $\hat{y}$, such that:

@@

Table \ref{table:node} shows the various node features with an example respectively.

@@

\section{Experiments/ Evaluation}
In the following section we present our experiments and the evalution of our system.
\subsection*{Experiments}

@@

\begin{table}[h!]
\scriptsize
\begin{tabular}{l |l| l| l| l| l| l}

\bf Language & \multicolumn{3}{c|}{ \bf testA}&\multicolumn{3}{c}{ \bf testB}\\\hline 
             & Precision & Recall & $F_1$ & Precision & Recall & $F_1$ \\ \hline
Spanish &       &          &     &          &               & \\
Dutch  &         &          &     &          &               &   \\
English &        &          &     &          &               &       \\
German &      &          &       &          &             & \\
\end{tabular}
\caption{NER Structured Prediction Results }
\label{table:Results}
\end{table}

>>>>

\documentclass[11pt]{article}
\usepackage{acl2011}
\usepackage[utf8]{inputenc}
\usepackage{linguex}
\usepackage{latexsym}  
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{verbatim}
\usepackage{array}
\usepackage{subfigure}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{qtree}

@@

\begin{figure*}[ht]

@@

\exg. \textbf{x:} The motor company ' Ford ' was founded and incorporated by Henry Ford .\\
      \textbf{y:} O O O O ORG  O  O O O O O PER PER O  \label{PredEx1b} \\
\caption{Input and predicted structure for the Named Entity task.}

\end{figure*}

@@

Learning is implemented using the Structured Perceptron algorithm. To avoid overfitting, we average the parameters after the last iteration \cite{collins2002discriminative}. For finding the best sequence of labels for a sentence, we use a modified version of the Viterbi algorithm. The algorithm finds the sequence $\hat{y}$, such that:

@@

Table~\ref{table:node} shows the various node features with an example respectively.

@@

\section{Experiments and Evaluation}
In the following section we present our experiments and the evalution of our system.
\subsection*{Experiments}

@@

\begin{table}[h!]
\scriptsize
\begin{tabular}{| l | l l l| l l l |}

\hline
\bf Language & \multicolumn{3}{c|}{ \bf Test A}&\multicolumn{3}{c|}{ \bf Test B}\\
             & Precision & Recall & $F_1$ & Precision & Recall & $F_1$ \\ \hline
Spanish &       &          &     &          &               & \\
Dutch  &         &          &     &          &               &   \\
English &        &          &     &          &               &       \\
German &      &          &       &          &             & \\
\hline
\end{tabular}
\caption{NER Structured Prediction Results }
\label{table:Results}
\end{table}
